### 2008-03-17 SAiP/Module1/H3/doc/architecturaldescription.tex
Adding spell-check

The architect for a new Beer Web Store for specialty beers has drawn
the following figure of the architecture together with his customers.
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/beerstore,scale=0.30,clip=true}}
\end{figure}
The system is to support web users that may purchase beers using a web
browser. The system runs on top of a database (``DB''), contains
domain model (``Data''), an overview page (``Overview''), and a
``Basket'' subpart.

@@

Another perspective is that the users, the webserver and the
database are elements where the relations show that the users
use the webserver and the webserver uses the database. This
also shows the that the architecture is a
\emph{strictly layered structure} where the users cannot
access the database directly.

@@

As there are several users, the elements of the
\emph{strictly layered structure} can also be seen as a
\emph{client-server structure}, where the users are clients
and the webserver is a server. The webserver can also be
seen as a client to the database server. This would make it
possible to archieve better performance if several webservers
are used to make load balancing of the user requests.

@@

With regard to a \emph{deployment structure}, the figure shows
that the overview page, the basket and the domain model (elements)
are allocated to (relations) on the webserver and the database is
allocated to its own server.

@@

These viewpoints are all relevant to the Beer Web Store example.
The Module viewpoint describes the internals of the webserver and how
the functionality is decomposed into units. The Component \& connector
viewpoint describes the runtime relations between the units and the
Allocation viewpoint describes the environment of the running
system.

@@

Figure \ref{fig:ad_package} shows a package diagram of the Beer Web
Store and a decomposition of the web package. The Web package
contains the elements used for the web interface, 
the Overview page, the basket and the domain model. The domain model
depends on a Database package that contains the database facade and the
database facade uses some database package library, e.g. MySQL.

@@

The domain model accesses the database through the database facade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment should
also be made.

@@

The application code (Beer Web) and the database facade are
both deployed on the web server.

@@

The benifits of a box-and-line drawing is that it can be written and "understood" by almost anyone, and in the initial phases of the architectual design they may be fine. They are fast to draw and can be shown to non-technical stakeholders. It is kind of like simple sign-language - everyone understands nodding and shaking ones head or indicating a direction as long as it is for general information.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambigious quantifiability. For this a clearly defined modeling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguaty of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambigious modelling language known by all stakeholders, and when that is the case it may be more confusing then benificial to spend time making sure the diagram is clear and unambigious, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

@@

As SOA consists of a collection of (preferrably stateless) well-defined services what needs to be described is, which existing (external) services are needed and which new services has to be created. This may be done using the MacKenzie Topic maps, which describe the static dependencies between the services.

>>>>

The architect for a new Beer Web Store for speciality beers has drawn
the following figure of the architecture together with his customers.
\begin{figure}[h!]
  \centerline{\epsfig{figure=figures/beerstore,scale=0.30,clip=true}}
\end{figure}
The system is to support web users that may purchase beers using a web
browser. The system runs on top of a database (``DB''), contains
domain model (``Data''), an overview page (``Overview''), and a
``Basket'' subpart.

@@

Another perspective is that the users, the web server and the
database are elements where the relations show that the users
use the web server and the web server uses the database. This
also shows the that the architecture is a
\emph{strictly layered structure} where the users cannot
access the database directly.

@@

As there are several users, the elements of the
\emph{strictly layered structure} can also be seen as a
\emph{client-server structure}, where the users are clients
and the web server is a server. The web server can also be
seen as a client to the database server. This would make it
possible to achieve better performance if several web servers
are used to make load balancing of the user requests.

@@

With regard to a \emph{deployment structure}, the figure shows
that the overview page, the basket and the domain model (elements)
are allocated to (relations) on the web server and the database is
allocated to its own server.

@@

These viewpoints are all relevant to the Beer Web Store example.
The Module viewpoint describes the internals of the web server and how
the functionality is decomposed into units. The Component \& connector
viewpoint describes the runtime relations between the units and the
Allocation viewpoint describes the environment of the running
system.

@@

Figure \ref{fig:ad_package} shows a package diagram of the Beer Web
Store and a decomposition of the web package. The Web package
contains the elements used for the web interface, 
the Overview page, the basket and the domain model. The domain model
depends on a Database package that contains the database fa\c ade and the
database fa\c ade uses some database package library, e.g. MySQL.

@@

The domain model accesses the database through the database fa\c ade
when needed. This can be expressed in another sequence diagram.
Sequence diagrams showing the checkout including payment should
also be made.

@@

The application code (Beer Web) and the database fa\c ade are
both deployed on the web server.

@@

The benefits of a box-and-line drawing is that it can be written and "understood" by almost anyone, and in the initial phases of the architectural design they may be fine. They are fast to draw and can be shown to non-technical stakeholders. It is kind of like simple sign-language - everyone understands nodding and shaking ones head or indicating a direction as long as it is for general information.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambiguous quantifiable. For this a clearly defined modelling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguity of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambiguous modelling language known by all stakeholders, and when that is the case it may be more confusing then beneficial to spend time making sure the diagram is clear and unambiguous, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

@@

As SOA consists of a collection of (preferably stateless) well-defined services what needs to be described is, which existing (external) services are needed and which new services has to be created. This may be done using the MacKenzie Topic maps, which describe the static dependencies between the services.
